Multiset-trie data structure

### 2023-02-22 tex/tex/s_experiments.tex
all reviewers comments answered.

%Performance of the functions will be measured by 
%the number of visited nodes in multiset-trie by the particular function. In 
%particular the performance is inversely proportional to the number of visited 
%nodes.

@@

Implementations of the sub-multiset and super-multiset are similar in
the case of the inverted file. The algorithm consists of the same
steps. First, the postings are fetched for each element of the test
multiset. Depending on the particular operation, postings are filtered
on-the-fly. Finally, the union or the intersection of the filtered set
of postings is computed. Note that the processing time increases with
the size of the inverted index because of the increased sizes of
postings.

>>>>

The current implementation of multiset-trie is not optimized for space consumption.
A node in the multiset-trie is implemented as a record indicating the level of the tree
that corresponds to a symbol from $\Sigma$, and including an array of pointers to
its children indexed by the multiplicities of the child symbols. The arrays have
fixed length $n$ from the interval $[0,n].$
Only some elements of an array may point to a child node, while others include
$Null$ value.

% Performance of the functions will be measured by 
%the number of visited nodes in multiset-trie by the particular function. In 
%particular the performance is inversely proportional to the number of visited 
%nodes.

@@

Implementations of the multiset containment operations
for searching sub-multisets and super-multisets are similar in
the case of the inverted file. The algorithm consists of the same
steps. First, the postings are fetched for each element of the test
multiset. Depending on the particular operation, postings are filtered
on-the-fly. Finally, the union or the intersection of the filtered set
of postings is computed. Note that the processing time increases with
the size of the inverted index because of the increased sizes of
postings.

### 2023-02-22 tex/tex/s_operations.tex
all reviewers comments answered.

\subsection{Sub-multiset and super-multiset existence}
\label{s:subexists} \label{s:superexists}
The functions \textsc{submsetExistence} and \textsc{supermsetExistence} are
symmetrical in the following sense. Let a multiset $m$ represent the borderline
in $\mathcal{M}$ defined by a path from the root to a leaf by following
the elements from $m$. The operation \textsc{submsetExistence} searches
the left part of $\mathcal{M}$ and the operation \textsc{supermsetExistence}
the right part of $\mathcal{M}$.

@@

%\subsection{Super-multiset existence} \label{s:superexists}
The function \textsc{supermsetExistence}($\mathcal{M},m,dev$) checks if there 
exists super-multiset $x$ of a given multiset $m$ in $\mathcal{M},$ such that 
condition $| x[i] - m[i] |\leq dev$ is satisfied, where $1\leq i \leq \sigma.$
Symmetrically to the function \textsc{submsetExistence}, the function
\textsc{supermsetExistence} searches first for an exact match $x=m$ in
$\mathcal{M}.$ If such $x$ does not exist in $\mathcal{M},$ then
the function searches on the right side of the borderline (an exact match)
defined by $m$. Since we would like to find the closest (the smallest)
super-multiset we increase the multiplicity of elements in $m$ at every
level of $\mathcal(M)$ starting with the multiplicities of $m.$
The function \textsc{supermsetExistence} is presented in
Algorithm~\ref{alg:superxists}.

>>>>

\subsection{Sub-multiset and super-multiset existence}
\label{s:subexists} \label{s:superexists}
The functions \textsc{submsetExistence} and \textsc{supermsetExistence} are
symmetrical in the following sense. Let a multiset $m$ represent the borderline
in $\mathcal{M}$ defined by a path from the root to a leaf following
the elements from $m$. The operation \textsc{submsetExistence} searches
the left part of $\mathcal{M}$ and the operation \textsc{supermsetExistence}
the right part of $\mathcal{M}$.

@@

%\subsection{Super-multiset existence} \label{s:superexists}
The function \textsc{supermsetExistence}($\mathcal{M},m,dev$) checks if there 
exists super-multiset $x$ of a given multiset $m$ in $\mathcal{M},$ such that 
condition $| x[i] - m[i] |\leq dev$ is satisfied, where $1\leq i \leq \sigma.$
Symmetrically to the function \textsc{submsetExistence}, the function
\textsc{supermsetExistence} searches first for an exact match $x=m$ in
$\mathcal{M}.$ If such $x$ does not exist in $\mathcal{M},$ then
the function searches on the right side of the borderline representing
an exact match of $m$ in $\mathcal{M}.$ Since we would like to find
the closest (the smallest) super-multiset we increase the multiplicity of
elements in $m$ at every level of $\mathcal(M)$ starting with
the multiplicities of $m.$ The function \textsc{supermsetExistence}
is presented in Algorithm~\ref{alg:superxists}.
